Influence of Connectivity on Dung Beetle Communities

### 2025-06-11 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
cite

Biodiversity between patch types was compared using Hill numbers, a set of indexes developed with the goal of providing a unifying context for the quantification of the many ways we measure biodiversity [@jost_entropy_2006]. They are an alternative to more specialized metrics such as alpha, beta, and gamma diversities while being more standardized than other indexes such as Renyi or HCDT entropies, of which both groups of metrics are less intuitive for interpretation. Hill numbers are now the preferred metric for describing community dynamics for two reasons.  First, they are extrapolated from the same equation, manipulating a single parameter (i.e., _q_) to arrive at estimates of richness and diversity. Second, by  manipulating _q_ we can gain an understanding of compositional shifts otherwise obscured while using species richness [@chao_rarefaction_2014]. We compared community composition by increasing magnitudes of diversity components (i.e., _qD_) of _0D_ (i.e., species richness), _1D_ (i.e., Shannon entropy), and _2D_ (i.e, Simpson Diversity). <!--[can you add a sentence about how these are calculated? by which I mean - are the calculations different than for richness, shannon, etc.?]--> Diversity numbers and species richness were calculated using the package `hill` **(citation)** for the R statistical programming language  **(citation)**. Diversity numbers were calculated using package `iNEXT` [@hsieh_inext_2016]. Bray-Curtis dissimilarity values were calculated using package `Vegan` **(citation)**. Dung beetles were assigned traits by waste removal guild and habitat preference.

>>>>

Biodiversity between patch types was compared using Hill numbers, a set of indexes developed with the goal of providing a unifying context for the quantification of the many ways we measure biodiversity [@jost_entropy_2006]. They are an alternative to more specialized metrics such as alpha, beta, and gamma diversities while being more standardized than other indexes such as Renyi or HCDT entropies, of which both groups of metrics are less intuitive for interpretation. Hill numbers are now the preferred metric for describing community dynamics for two reasons.  First, they are extrapolated from the same equation, manipulating a single parameter (i.e., _q_) to arrive at estimates of richness and diversity. Second, by  manipulating _q_ we can gain an understanding of compositional shifts otherwise obscured while using species richness [@chao_rarefaction_2014]. We compared community composition by increasing magnitudes of diversity components (i.e., _qD_) of _0D_ (i.e., species richness), _1D_ (i.e., Shannon entropy), and _2D_ (i.e, Simpson Diversity). <!--[can you add a sentence about how these are calculated? by which I mean - are the calculations different than for richness, shannon, etc.?]--> Diversity numbers and species richness were calculated using the package `hill` [@li_hillr_2018] for the R statistical programming language  **(citation)**. Diversity numbers were calculated using package `iNEXT` [@hsieh_inext_2016]. Bray-Curtis dissimilarity values were calculated using package `Vegan` [@oksanen_vegan_2025]. Dung beetles were assigned traits by waste removal guild and habitat preference.
